---
title: "Tabby Extension"
format: 
  html:
    toc: false
filters:
- tabby
---

Tabby is a Quarto extension that automatically creates tabsets for code blocks, making it easy to present multiple programming language implementations side by side. It leverages Quarto's Tabset API to create an integrated tabbing experience.

## Installation

To install Tabby, run the following command in your project directory:

```bash
quarto add coatless-quarto/tabby
```

This will install the extension under the `_extensions` subdirectory. If you're using version control, you will want to check in this directory.

## Usage

### Setup

Add the filter to your document's YAML header or your project's `_quarto.yml` file:

```yaml
filters:
  - tabby
```

### Basic Example

Create a tabset by wrapping code blocks in a div with the `tabby` class:

````markdown
::: {.tabby}
```{{python}}
print("Hello, Python World!")
```

```javascript
console.log("Hello, JavaScript World!");
```

```{{r}}
print("Hello, R World!")
```
:::
````

This will automatically create a tabset with three tabs: "Python", "Javascript", and "R", each containing the respective code and, where applicable, its output.

::: {.tabby}
```{python}
print("Hello, Python World!")
```

```javascript
console.log("Hello, JavaScript World!");
```

```{r}
print("Hello, R World!")
```
:::

### Default Tab Selection

You can set the default selected tab in three ways, listed in order of precedence (highest to lowest):

1. **URL Parameter** - Add `?default-tab=python` to your URL
   ```default
   https://example.com/document.html?default-tab=python
   ```

2. **Individual Tabset** - Use div attributes:
   ```markdown
   ::: {.tabby default-tab="javascript"}
   ...
   :::
   ```

3. **Document Level** - Set in YAML frontmatter:
   ```yaml
   tabby:
     default-tab: python
   ```

### Tab Groups

Synchronize tab selection across multiple tabsets using the `group` attribute, similar to [Quarto Tabsets](https://quarto.org/docs/output-formats/html-basics.html#tabset-groups):

````markdown
::: {.tabby group="mygroup"}
```{{python}}
def greet():
    print("Hello!")
```

```{{r}}
greet <- function() {
  cat("Hello!\n");
}
```
:::

Some text in between...

::: {.tabby group="mygroup"}
```{{python}}
greet()
```

```{{r}}
greet()
```
:::
````

When you switch tabs in one tabset, all tabsets in the same group will switch to the same language.


::: {.tabby group="mygroup"}
```{python}
def greet():
    print("Hello!")
```

```{r}
greet <- function() {
  cat("Hello!\n");
}
```
:::

Some text in between...

::: {.tabby group="mygroup"}
```{python}
greet()
```

```{r}
greet()
```
:::

## Configuration Options

| Option | Description | Default | Example |
|--------|-------------|---------|----------|
| `default-tab` | Sets the default selected tab | `1` | `python`, `r`, `javascript` |
| `group` | Groups tabs across multiple tabsets | `null` | `"mygroup"` |

Configure options in your document's YAML frontmatter:

```yaml
tabby:
  default-tab: python    # Default tab selection
```
